Different rules for binocular combination of luminance in cortical and subcortical pathways

### 2022-09-28 manuscript.Rmd
Minor changes and added pupillometry analysis

## Apparatus & Stimuli
The stimuli were two discs of flickering light with a diameter of 3.74 degrees, presented on a black background. The same stimuli were used for all three experiments. Four dark red lines were added around both discs to help with their fusion into one binocular disc. Figure 1 shows an example of the of the unfused stimuli. The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors and so did not suffer from internal reflections, and allowed participants to see only one fused disc. The use of a stereoscope allowed us to display the stimuli in three different ocular configurations: monocular, binocular, and dichoptic.

@@

EEG data were collected for experiments 1 and 2 sampled at 1 kHz using a 64-electrode ANT WaveGuard cap and the signals were recorded using the ASA software (ANT Neuro, Hengelo, NL, United States). Pupillometry data were collected only for experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH) running at 120 Hz and the signals were recorded with the Pupil Capture software (Pupil Labs GmbH).

@@

As already stated, the mirror stereoscope allowed the use of three different ocular configurations. In the monocular configuration, one disc was set to flicker either at 2 Hz or 1.6 Hz for each contrast level, while the other disc remained stable at a constant mean luminance. In the binocular configuration, both discs flickered at the same contrast level with both discs flickering at 2 Hz in the same-frequency condition, while, in the cross-frequency condition, one disc flickered at 2 Hz and the other at 1.6 Hz. Finally, in the dichoptic configuration, one disc flickered across all contrast levels and the other flickered at a fixed contrast level that was set at 48 %. Similar to the binocular configuration, the dichoptic configuration was divided in same-frequency and cross-frequency conditions.

@@

>>>>

## Apparatus & Stimuli
The stimuli were two discs of flickering light with a diameter of 3.74 degrees, presented on a black background. The same stimuli were used for all three experiments. Four dark red lines were added around both discs to help with their fusion into one binocular disc (see insert in figure \@ref(fig:pupildata)a for an example of the of the fused stimuli). The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors and so did not suffer from internal reflections, and allowed participants to see only one fused disc. The use of a stereoscope allowed us to display the stimuli in three different ocular configurations: monocular, binocular, and dichoptic.

@@

EEG data were collected for experiments 1 and 2 sampled at 1 kHz using a 64-electrode ANT WaveGuard cap and the signals were recorded using the ASA software (ANT Neuro, Hengelo, NL, United States). Pupillometry data were collected only for experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, @Kassner2014) running at 120 Hz and the signals were recorded with the Pupil Capture software (Pupil Labs GmbH, @Kassner2014).

@@

As already stated, the mirror stereoscope allowed the use of three different ocular configurations. In the monocular configuration, one disc was set to flicker either at 2 Hz or 1.6 Hz for each contrast level, while the other disc remained stable at a constant mean luminance. In the binocular configuration, both discs flickered at the same contrast level with both discs flickering at 2 Hz in the same-frequency condition, while, in the cross-frequency condition, one disc flickered at 2 Hz and the other at 1.6 Hz. Finally, in the dichoptic configuration, one disc flickered across all contrast levels and the other flickered at a fixed contrast level that was set at 48 \%. Similar to the binocular configuration, the dichoptic configuration was divided in same-frequency and cross-frequency conditions.

@@

A similar process was adopted for the analysis of the pupillometry data. The data were converted from the mp4 format to a compressed csv text file using the Pupil Player software [@Kassner2014]. The individual data were then loaded into R for analysis where a twelve-second waveform for each trial in each eye was extracted. Fourier transform was calculated for each waveform, and the spectrum stored in a matrix. All repetitions of each condition were then averaged for each eye. They were then averaged across the two eyes, to obtain individual results. Finally, these were averaged across all participants to obtain the final results.

### 2022-09-28 manuscript.tex
Minor changes and added pupillometry analysis

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Different rules for binocular combination of luminance in cortical and subcortical pathways},
  pdfauthor={Federico G. Segala, Aurelio Bruno, Alex R. Wade \& Daniel H. Baker (+Myat? +Joel?)},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}

\title{Different rules for binocular combination of luminance in cortical and subcortical pathways}
\author{Federico G. Segala, Aurelio Bruno, Alex R. Wade \& Daniel H. Baker (+Myat? +Joel?)}
\date{2022-09-27}

@@

The stimuli were two discs of flickering light with a diameter of 3.74 degrees, presented on a black background. The same stimuli were used for all three experiments. Four dark red lines were added around both discs to help with their fusion into one binocular disc. Figure 1 shows an example of the of the unfused stimuli. The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors and so did not suffer from internal reflections, and allowed participants to see only one fused disc. The use of a stereoscope allowed us to display the stimuli in three different ocular configurations: monocular, binocular, and dichoptic.

@@

EEG data were collected for experiments 1 and 2 sampled at 1 kHz using a 64-electrode ANT WaveGuard cap and the signals were recorded using the ASA software (ANT Neuro, Hengelo, NL, United States). Pupillometry data were collected only for experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH) running at 120 Hz and the signals were recorded with the Pupil Capture software (Pupil Labs GmbH).

@@

@@

The results from the second experiment are shown in figure \ref{fig:TFdata}. In figures 5A to 5C, the curves are showing the results for the monocular and the binocular configurations. In figure 5D, the curves are showing the results for the two harmonics.

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Anderson1989}{}%
Anderson PA, Movshon JA. 1989. Binocular combination of contrast signals. \emph{Vision Res} \textbf{29}:1115--32. doi:\href{https://doi.org/10.1016/0042-6989(89)90060-6}{10.1016/0042-6989(89)90060-6}

\leavevmode\hypertarget{ref-Angee2021}{}%
Angée C, Nedelec B, Erjavec E, Rozet J-M, Fares Taie L. 2021. Congenital microcoria: Clinical features and molecular genetics. \emph{Genes (Basel)} \textbf{12}. doi:\href{https://doi.org/10.3390/genes12050624}{10.3390/genes12050624}

\leavevmode\hypertarget{ref-Anstis1998}{}%
Anstis S, Ho A. 1998. Nonlinear combination of luminance excursions during flicker, simultaneous contrast, afterimages and binocular fusion. \emph{Vision Res} \textbf{38}:523--39. doi:\href{https://doi.org/10.1016/s0042-6989(97)00167-3}{10.1016/s0042-6989(97)00167-3}

\leavevmode\hypertarget{ref-Baker2018}{}%
Baker DH, Lygo FA, Meese TS, Georgeson MA. 2018. Binocular summation revisited: Beyond \(\sqrt{2}\). \emph{Psychol Bull} \textbf{144}:1186--1199. doi:\href{https://doi.org/10.1037/bul0000163}{10.1037/bul0000163}

\leavevmode\hypertarget{ref-Campbell1965}{}%
Campbell FW, Green DG. 1965. Monocular versus binocular visual acuity. \emph{Nature} \textbf{208}:191--2. doi:\href{https://doi.org/10.1038/208191a0}{10.1038/208191a0}

\leavevmode\hypertarget{ref-Delorme2004}{}%
Delorme A, Makeig S. 2004. EEGLAB: An open source toolbox for analysis of single-trial eeg dynamics including independent component analysis. \emph{J Neurosci Methods} \textbf{134}:9--21. doi:\href{https://doi.org/10.1016/j.jneumeth.2003.10.009}{10.1016/j.jneumeth.2003.10.009}

\leavevmode\hypertarget{ref-Ding2006}{}%
Ding J, Sperling G. 2006. A gain-control theory of binocular combination. \emph{Proc Natl Acad Sci U S A} \textbf{103}:1141--6. doi:\href{https://doi.org/10.1073/pnas.0509629103}{10.1073/pnas.0509629103}

\leavevmode\hypertarget{ref-Legge1984}{}%
Legge GE. 1984. Binocular contrast summation--ii. Quadratic summation. \emph{Vision Res} \textbf{24}:385--94. doi:\href{https://doi.org/10.1016/0042-6989(84)90064-6}{10.1016/0042-6989(84)90064-6}

\leavevmode\hypertarget{ref-Levelt1965}{}%
Levelt WJ. 1965. BINOCULAR brightness averaging and contour information. \emph{Br J Psychol} \textbf{56}:1--13. doi:\href{https://doi.org/10.1111/j.2044-8295.1965.tb00939.x}{10.1111/j.2044-8295.1965.tb00939.x}

\leavevmode\hypertarget{ref-Mathot2018}{}%
Mathôt S. 2018. Pupillometry: Psychology, physiology, and function. \emph{J Cogn} \textbf{1}:16. doi:\href{https://doi.org/10.5334/joc.18}{10.5334/joc.18}

\leavevmode\hypertarget{ref-McDougal2010}{}%
McDougal DH, Gamlin PD. 2010. The influence of intrinsically-photosensitive retinal ganglion cells on the spectral sensitivity and response dynamics of the human pupillary light reflex. \emph{Vision Res} \textbf{50}:72--87. doi:\href{https://doi.org/10.1016/j.visres.2009.10.012}{10.1016/j.visres.2009.10.012}

\leavevmode\hypertarget{ref-Meese2006}{}%
Meese TS, Georgeson MA, Baker DH. 2006. Binocular contrast vision at and above threshold. \emph{J Vis} \textbf{6}:1224--43. doi:\href{https://doi.org/10.1167/6.11.7}{10.1167/6.11.7}

\leavevmode\hypertarget{ref-Purves2008}{}%
Purves D, Brannon EM, Cabeza R, LaBar KS, Huettel SA, Platt ML, Woldorff MG. 2008. Principles of Cognitive Neuroscience. Oxford University Press, Incorporated.

\leavevmode\hypertarget{ref-Wang2015}{}%
Wang C-A, Munoz DP. 2015. A circuit for pupil orienting responses: Implications for cognitive modulation of pupil size. \emph{Curr Opin Neurobiol} \textbf{33}:134--40. doi:\href{https://doi.org/10.1016/j.conb.2015.03.018}{10.1016/j.conb.2015.03.018}

\leavevmode\hypertarget{ref-Wyatt1981}{}%
Wyatt HJ, Musselman JF. 1981. Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem. \emph{Vision Res} \textbf{21}:513--25. doi:\href{https://doi.org/10.1016/0042-6989(81)90097-3}{10.1016/0042-6989(81)90097-3}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Different rules for binocular combination of luminance in cortical and subcortical pathways},
  pdfauthor={Federico G. Segala, Aurelio Bruno, Alex R. Wade \& Daniel H. Baker (+Myat? +Joel?)},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Different rules for binocular combination of luminance in cortical and subcortical pathways}
\author{Federico G. Segala, Aurelio Bruno, Alex R. Wade \& Daniel H. Baker (+Myat? +Joel?)}
\date{2022-09-28}

@@

The stimuli were two discs of flickering light with a diameter of 3.74 degrees, presented on a black background. The same stimuli were used for all three experiments. Four dark red lines were added around both discs to help with their fusion into one binocular disc (see insert in figure \ref{fig:pupildata}a for an example of the of the fused stimuli). The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors and so did not suffer from internal reflections, and allowed participants to see only one fused disc. The use of a stereoscope allowed us to display the stimuli in three different ocular configurations: monocular, binocular, and dichoptic.

@@

EEG data were collected for experiments 1 and 2 sampled at 1 kHz using a 64-electrode ANT WaveGuard cap and the signals were recorded using the ASA software (ANT Neuro, Hengelo, NL, United States). Pupillometry data were collected only for experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Kassner et al. (2014)) running at 120 Hz and the signals were recorded with the Pupil Capture software (Pupil Labs GmbH, Kassner et al. (2014)).

@@

A similar process was adopted for the analysis of the pupillometry data. The data were converted from the mp4 format to a compressed csv text file using the Pupil Player software (Kassner et al., 2014). The individual data were then loaded into R for analysis where a twelve-second waveform for each trial in each eye was extracted. Fourier transform was calculated for each waveform, and the spectrum stored in a matrix. All repetitions of each condition were then averaged for each eye. They were then averaged across the two eyes, to obtain individual results. Finally, these were averaged across all participants to obtain the final results.

@@

The results from the second experiment are shown in figure \ref{fig:TFdata}. Figure \ref{fig:TFdata}a is showing the fourier spectra

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Anderson1989}{}}%
Anderson PA, Movshon JA. 1989. Binocular combination of contrast signals. \emph{Vision Res} \textbf{29}:1115--32. doi:\href{https://doi.org/10.1016/0042-6989(89)90060-6}{10.1016/0042-6989(89)90060-6}

\leavevmode\vadjust pre{\hypertarget{ref-Angee2021}{}}%
Angée C, Nedelec B, Erjavec E, Rozet J-M, Fares Taie L. 2021. Congenital microcoria: Clinical features and molecular genetics. \emph{Genes (Basel)} \textbf{12}. doi:\href{https://doi.org/10.3390/genes12050624}{10.3390/genes12050624}

\leavevmode\vadjust pre{\hypertarget{ref-Anstis1998}{}}%
Anstis S, Ho A. 1998. Nonlinear combination of luminance excursions during flicker, simultaneous contrast, afterimages and binocular fusion. \emph{Vision Res} \textbf{38}:523--39. doi:\href{https://doi.org/10.1016/s0042-6989(97)00167-3}{10.1016/s0042-6989(97)00167-3}

\leavevmode\vadjust pre{\hypertarget{ref-Baker2018}{}}%
Baker DH, Lygo FA, Meese TS, Georgeson MA. 2018. Binocular summation revisited: Beyond \(\sqrt{2}\). \emph{Psychol Bull} \textbf{144}:1186--1199. doi:\href{https://doi.org/10.1037/bul0000163}{10.1037/bul0000163}

\leavevmode\vadjust pre{\hypertarget{ref-Campbell1965}{}}%
Campbell FW, Green DG. 1965. Monocular versus binocular visual acuity. \emph{Nature} \textbf{208}:191--2. doi:\href{https://doi.org/10.1038/208191a0}{10.1038/208191a0}

\leavevmode\vadjust pre{\hypertarget{ref-Delorme2004}{}}%
Delorme A, Makeig S. 2004. EEGLAB: An open source toolbox for analysis of single-trial EEG dynamics including independent component analysis. \emph{J Neurosci Methods} \textbf{134}:9--21. doi:\href{https://doi.org/10.1016/j.jneumeth.2003.10.009}{10.1016/j.jneumeth.2003.10.009}

\leavevmode\vadjust pre{\hypertarget{ref-Ding2006}{}}%
Ding J, Sperling G. 2006. A gain-control theory of binocular combination. \emph{Proc Natl Acad Sci U S A} \textbf{103}:1141--6. doi:\href{https://doi.org/10.1073/pnas.0509629103}{10.1073/pnas.0509629103}

\leavevmode\vadjust pre{\hypertarget{ref-Kassner2014}{}}%
Kassner M, Patera W, Bulling A. 2014. Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interactionProceedings of the 2014 {ACM} International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication. UbiComp '14 Adjunct; {ACM}. pp. 1151--1160. doi:\href{https://doi.org/10.1145/2638728.2641695}{10.1145/2638728.2641695}

\leavevmode\vadjust pre{\hypertarget{ref-Legge1984}{}}%
Legge GE. 1984. Binocular contrast summation--II. Quadratic summation. \emph{Vision Res} \textbf{24}:385--94. doi:\href{https://doi.org/10.1016/0042-6989(84)90064-6}{10.1016/0042-6989(84)90064-6}

\leavevmode\vadjust pre{\hypertarget{ref-Levelt1965}{}}%
Levelt WJ. 1965. BINOCULAR BRIGHTNESS AVERAGING AND CONTOUR INFORMATION. \emph{Br J Psychol} \textbf{56}:1--13. doi:\href{https://doi.org/10.1111/j.2044-8295.1965.tb00939.x}{10.1111/j.2044-8295.1965.tb00939.x}

\leavevmode\vadjust pre{\hypertarget{ref-Mathot2018}{}}%
Mathôt S. 2018. Pupillometry: Psychology, physiology, and function. \emph{J Cogn} \textbf{1}:16. doi:\href{https://doi.org/10.5334/joc.18}{10.5334/joc.18}

\leavevmode\vadjust pre{\hypertarget{ref-McDougal2010}{}}%
McDougal DH, Gamlin PD. 2010. The influence of intrinsically-photosensitive retinal ganglion cells on the spectral sensitivity and response dynamics of the human pupillary light reflex. \emph{Vision Res} \textbf{50}:72--87. doi:\href{https://doi.org/10.1016/j.visres.2009.10.012}{10.1016/j.visres.2009.10.012}

\leavevmode\vadjust pre{\hypertarget{ref-Meese2006}{}}%
Meese TS, Georgeson MA, Baker DH. 2006. Binocular contrast vision at and above threshold. \emph{J Vis} \textbf{6}:1224--43. doi:\href{https://doi.org/10.1167/6.11.7}{10.1167/6.11.7}

\leavevmode\vadjust pre{\hypertarget{ref-Purves2008}{}}%
Purves D, Brannon EM, Cabeza R, LaBar KS, Huettel SA, Platt ML, Woldorff MG. 2008. Principles of {Cognitive} {Neuroscience}. Oxford University Press, Incorporated.

\leavevmode\vadjust pre{\hypertarget{ref-Wang2015}{}}%
Wang C-A, Munoz DP. 2015. A circuit for pupil orienting responses: Implications for cognitive modulation of pupil size. \emph{Curr Opin Neurobiol} \textbf{33}:134--40. doi:\href{https://doi.org/10.1016/j.conb.2015.03.018}{10.1016/j.conb.2015.03.018}

\leavevmode\vadjust pre{\hypertarget{ref-Wyatt1981}{}}%
Wyatt HJ, Musselman JF. 1981. Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem. \emph{Vision Res} \textbf{21}:513--25. doi:\href{https://doi.org/10.1016/0042-6989(81)90097-3}{10.1016/0042-6989(81)90097-3}

\end{CSLReferences}
